\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{multicol}

% Page layout
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\setlength{\tabcolsep}{0in}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Custom commands
\newcommand{\resheading}[1]{\vspace{-5pt}\section*{\uppercase{#1}}\vspace{-6pt}}
\newcommand{\resitem}[1]{\item #1 \vspace{-4pt}}
\newcommand{\ressubheading}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
}
\newcommand{\ressubsubheading}[2]{
  \textbf{#1} \hfill \textit{#2}
}

\begin{document}

%-----------Heading-----------
\vspace{10pt}
\begin{center}
    {\LARGE \textbf{Swapnilshikha Bhakat}} \\
    \vspace{1pt}
    Ghatshila, Jharkhand • \href{mailto:bhakatswapnilshikha@gmail.com}{bhakatswapnilshikha@gmail.com} • +91-6200428337 \\
    \href{https://github.com/swapnilshikha}{github.com/swapnilshikha} • 
    \href{https://linkedin.com/in/swapnilshikha-bhakat-264221270}{linkedin.com/in/swapnilshikha} • 
    \href{https://swapnilshikha.xyz/}{swapnilshikha.xyz}
\end{center}

%-----------About-----------
\resheading{Profile}
\noindent
Final-year B.Tech Computer Science student with a passion for web development. Experienced in solving real-world problems through clean code and intuitive user experiences. Alongside academics, I actively contribute to college events, enhancing my leadership, collaboration, and time management skills.

%-----------Skills-----------
\resheading{Technical Skills}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, topsep=1pt]
  \item \textbf{Languages:} C, C++, Java, Python, JavaScript, SQL
  \item \textbf{Web:} HTML, CSS, React.js, Express.js, MongoDB, Node.js
  \item \textbf{Cloud/Tools:} AWS, GitHub, VS Code, Postman, Jupyter Notebook
  \item \textbf{CS Fundamentals:} DBMS, Operating Systems, Data Structures
\end{itemize}

%-----------Education-----------
\resheading{Education}
\begin{itemize}[leftmargin=0.15in, itemsep=4pt, topsep=1pt]
  \item \ressubheading{Silicon University}{Bhubaneswar, India}{B.Tech in Computer Science; CGPA: 9.02}{2022 – 2026 (Expected)}
  \item \ressubheading{St. Joseph’s Convent High School, Mosaboni}{Jharkhand}{Intermediate; 90.67\%}{2020 – 2021}
  \item \ressubheading{St. Joseph’s Convent High School, Mosaboni}{Jharkhand}{Matriculation; 94\%}{2018 – 2019}
\end{itemize}

%-----------Projects-----------
\resheading{Projects}
\begin{itemize}[leftmargin=0.15in, itemsep=8pt, topsep=1pt]

  \item \textbf{DrNextDoor (MERN Stack)} \hfill \href{https://github.com/swapnilshikha/DrNextDoor}{GitHub Link}
  \begin{itemize}[itemsep=2pt, topsep=1pt]
    \resitem{Built a responsive Home Page in React.js with doctor listings and appointment booking.}
    \resitem{Created a secure Admin Panel using Express.js and MongoDB.}
    \resitem{Tested backend REST APIs with Postman for robust communication.}
  \end{itemize}

  \item \textbf{AWS VPC Project} \hfill \href{https://github.com/swapnilshikha/AWS-Project}{GitHub Link}
  \begin{itemize}[itemsep=2pt, topsep=1pt]
    \resitem{Designed a VPC with public/private subnets for secure AWS deployment.}
    \resitem{Used Application Load Balancer and Route 53 for traffic management.}
    \resitem{Enabled Auto Scaling for performance optimization.}
  \end{itemize}

  \item \textbf{Burberry Clone Website} \hfill \href{https://coding-comandoes.github.io/Burberry-Clone/}{Live Link}
  \begin{itemize}[itemsep=2pt, topsep=1pt]
    \resitem{Built responsive fashion website clone using React.js, CSS, and Material UI.}
    \resitem{Implemented login page with form validation.}
    \resitem{Collaborated with team using GitHub for version control.}
  \end{itemize}

  \item \textbf{Crop Economy Prediction Model (ML)} \hfill \href{https://github.com/swapnilshikha/Climate_change_on_agriculture}{GitHub Link}
  \begin{itemize}[itemsep=2pt, topsep=1pt]
    \resitem{Developed a predictive model to assess the economic impact of climate change on Indian agriculture.}
    \resitem{Used Ridge, Lasso, Linear Regression, Decision Tree, and K-Nearest Neighbors (KNN).}
    \resitem{Strengthened Python and machine learning skills through model implementation and performance analysis.}
  \end{itemize}

  \item \textbf{Personal Portfolio Website} \hfill \href{https://swapnilshikha.xyz/}{Live Link}
  \begin{itemize}[itemsep=2pt, topsep=1pt]
    \resitem{Designed and deployed a personal portfolio using React.js and CSS.}
    \resitem{Added downloadable resume and contact form with email integration.}
    \resitem{Showcases key projects, skills, and links to GitHub/LinkedIn.}
  \end{itemize}

\end{itemize}

%-----------Achievements-----------
\resheading{Achievements}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt, topsep=1pt]
  \item Selected for Smart India Hackathon 2024 (College Level)
  \item Top Performer – AWS Internship Program
  \item 2nd Place – Debugging Event, “GEEK-O-FIRE 2.0” (ISTE Silicon Chapter)
  \item GDSC Content Writer (2023 – 2024)
  \item YFS Volunteer (2022 – 2023)
\end{itemize}

\end{document}

